\begin{enumerate}
\item \textbf{Mooring}:- This is the first activity where the vessel will be secured in order to load the turbine components and not weather dependent activity.
\item \textbf{Loading}:- The loading operation for each turbine component is dependent on the weather condition and it starts with tower loading, then nacelles loading and finally blades. It has both working and down time due to the weather condition.
\item \textbf{Unmooring}:- Once all the turbine components are loaded and the ship is ready to sail, the mooring system will be released and not weather dependent activity.
\item \textbf{Transportation}:- There should good weather condition during the sailing time and the longer the distance the higher the weather down time. In order to avoid long duration of weather window down time  for the transport phase, It has been split into two phases where a transition point will be considered between the port and the offshore site.
\item \textbf{Positioning and set up} :- At the offshore site, the vessel should be first properly positioned so as to carry out the installation activities and  additional set up activities are also required. It is weather dependent and the wave height is the dominant weather restriction factor for this section.

\item \textbf{Installation} :- As already mentioned in the previous section, the parts will be installed one by one based on the availability of good weather. The installation process is highly affected by the weather condition and the wind speed is the dominant factor. The installation time is  divided into two namely set up (preparation) time and installation time. 
\item \textbf{Jack Lowering} :- After completing the installation of one complete Offshore Wind turbine, the next step is jacking down and it is also weather dependent (wave height).
\item \textbf{Transportation} : This is the trip back to the port in order to load the remaining turbine components and similar procedure will be followed as the one to the offshore site mentioned in terms of weather time window. If all the turbines are installed , this will be the last activity of the discrete event simulation model.

\end{enumerate}